---
title: 'Review for Submission #3274'
subtitle: |
  Review of the Article *`sgmcmc`: An R Package for Stochastic Gradient Markov
  Chain Monte Carlo*, authored by Baker, Fearnhead, Fox & Nemeth and submitted to
  the *Journal of Statistical Software*
author: "Marcelo Ventura Freire *(`mvf@usp.br`)*"
date: "`r Sys.Date()`"
output: 
  pdf_document: 
    number_sections: yes
    toc: yes
    toc_depth: 4
bibliography: "myrefs.bib"
biblio-style: "jss.bst"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = TRUE)
```

# Introduction

As required by the editorial board of this Journal of Statistical Software, I proceeded to reviewing the submission identified above in three fronts: 

- one *article* review on the file `sgmcmc.pdf`; and 
- two *package* reviews on the contents of the file `sgmcmc_0.2.0.tar.gz`, taking into account the contents of the auxiliary file `reproduction_material.tar.gz`.

All three files above were analysed as provided by the editorial board.

As a disclaimer, I neither assessed the performance of the package nor conducted benchmarking tests with existing alternatives to stochastic gradient MCMC.

The result of the three independent reviews will be presented in what follows.

# Article Review

# Package Reviews

## Methodological Review

This review intends to assess whether or not the package succeeded implementing the SGMCMC samplers as proposed in the article.

### Sampler `sgld` -- Stochastic gradient Langevin dynamics

### Sampler `sghmc` -- Stochastic gradient Hamiltonian Monte Carlo

### Sampler `sgnht` -- Stochastic gradient Nosé-Hoover thermostat

### Sampler `sgldcv` -- Stochastic gradient Langevin dynamics with control variates

### Sampler `sghmccv` -- Stochastic gradient Hamiltonian Monte Carlo with control variates

### Sampler `sgnhtcv` -- Stochastic gradient Nosé-Hoover thermostat with control variates

## Package Mechanics Review

### Introduction

This review intends to assess whether or not the package organization is free of flaws, as well as whether or not the package attained a seamless integration with the external software *TensorFlow*.

At the moment I started this review, the *sgmcmc* package was already available online at [CRAN repository](https://cran.r-project.org/web/packages/sgmcmc/index.html) in its version 0.2.0 (the same I received from JSS editors) and its source was accessible in the [project's GitHub repository](https://github.com/STOR-i/sgmcmc).

I conducted this review with the following conditions:

- Hardware setting: 
    - Dell Inspiron 7520 laptop
    - Intel Core i7 processor with 8 cores
    - 8 Gb RAM
- Software setting:
    - Lubuntu version 17.10 with kernel version 4.13.0  [**???**]
    - Python version 3.6.3 [**???**]
    - TensorFlow version 1.4.0 [**???**]
- R setting:
    - R version 3.4.2 [@RLang]
    - package *tensorflow* version 1.4.1 [**???**]
    - RStudio IDE version 1.1.391  [**???**]

As a disclaimer, I did not test *sgmcmc* package with in the following particular conditions:

- in Windows or OSX operating systems;
- with Python 2; and
- with TensorFlow GPU capabilities.

As an online reference for this review, I considered the [*Review guide for analysis best practice*](https://docs.google.com/document/d/1OYcWJUk-MiM2C1TIHB1Rn6rXoF5fHwRX-7_C12Blx8g) from the [*rOpenSci Analysis Best Practice Guidelines*](https://github.com/ropenscilabs/checkers), developed at [*rOpenSci “Unconference” 2017*](http://unconf17.ropensci.org/).

### Organizational Aspects of the Package

#### Instalation

For starters, I tried to install **sgmcmc** directly from CRAN:

```{r check.install, width=60}
install.packages(
  "sgmcmc", 
  repos = "https://cloud.r-project.org",
  destdir = "install", 
  dependencies = T, 
  verbose = T
)
```

As it can be seen, I was able to install **sgmcmc** version 0.2.0 (the same version sent to me by the editors) directly from CRAN in Linux, so the package was able to build successfully.

Also, the file downloaded from CRAN and the file received from the editor are the same, as it should be expected and as it can be seen:

```{r diff, echo=TRUE, message=TRUE, warning=TRUE, error=TRUE}
system2(
  "bash", 
  " -c 'LC_ALL=c diff -s originals/sgmcmc_0.2.0.tar.gz install/sgmcmc_0.2.0.tar.gz'", 
  stdout = T
)
```

#### Documentation

#### Vignettes, Datasets and Examples

##### Vignette `sgmcmc` -- Getting Started

##### Function `getDataset()` and Datasets `covertype` and `mnist`

##### Vignette `gaussMixture` -- Gaussian Mixture

##### Vignette `logisticRegression` -- Logistic Regression

##### Vignette `mvGauss` -- Multivariate Gaussian

##### Vignette `nn` -- Bayesian Neural Network


### Integration with the library *TensorFlow*

As I previouly installed the package *tensorflow* and ran `tensorflow::install_tensorflow()`,


# Bibliography
<!-- Left blank for BibTeX output following -->
